---
title: "Composition to enzyme level analysis"
author: "Cankun Wang"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: false
    number_sections: true
    code_folding: hide
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
# Hide all warnings and messages, show code
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = F)

bioc_packages <- c("EnhancedVolcano")
cran_packages <- c("enrichR",
                   "ggpubr",
                   "pheatmap",
                   "ggplot2",
                   "VennDiagram",
                   "stringr",
                   "here")
bioc_np <-
  bioc_packages[!(bioc_packages %in% installed.packages()[, "Package"])]
cran_np <-
  cran_packages[!(cran_packages %in% installed.packages()[, "Package"])]


# 'here' pacakge automatically sets working directory for us
library(here)
# DESeq2 provides methods to test for differential gene expression (DGE) analysis 
library(DESeq2)
# ‘ggplot2’ and its extension for publication ready plots
library(ggplot2)
library(ggpubr) 
# Volcano plot
#library(EnhancedVolcano) 
# Heatmap
library(pheatmap) 
# enrichR provides functional gene set enrichment analysis
library(enrichR) 
library(patchwork)

#library(phyloseq)

theme_set(theme_bw())
fontsize = 18L
theme_update(axis.title.x = element_text(size=fontsize))
theme_update(axis.title.y = element_text(size=fontsize))
theme_update(plot.title = element_text(size=fontsize+2))
#library(lefser)
library(Seurat)
library(tidyverse)
```

# Task

Enzyme search page: https://enzyme.expasy.org/enzyme-search-ec.html

Composition to enzyme level.

Steps:

1. Subset the total enzyme-sample matrix based on 'Supplementary Table 1: List of sulfur-metabolizing or modifying enzymes'

2. Perform differential analysis on three groups: pre- vs post-RYGB, pre- vs post-VSG, and men with RYGB _SWL vs women with RYGB_SWL


# Load data

Sample 126, 128, 129, 131, 132, 139 are removed from analysis

```{r}

counts <- read.csv("gene_family_uniref90_level4ec_subset.csv", row.names = 1)
count2 <- counts %>%
  rownames_to_column("id")
# Read metadata
meta <- read.csv("meta_v2.csv", stringsAsFactors = F)
remove_idx <- which(meta$ID %in% c(126, 128, 129, 131, 132, 139))

counts <- counts[, -remove_idx]
meta <- meta[-remove_idx,]

surg <- str_split_fixed(meta$surg_and_wtloss, "\\+", 2)[,1]
wtloss <- str_split_fixed(meta$surg_and_wtloss, "\\+", 2)[,2]
wtloss <-gsub("^$","Pre-surgery", wtloss)

#write.csv(count_py, "enzyme_py.csv", row.names = T, col.names = F, quote = F)
#write.table(count_py, "enzyme_py.txt", row.names = T, col.names = F, quote = F, sep="\t")

all_species <- data.frame(name=rownames(counts))

enzyme_list <- read_lines("./humann_gene_family/selected_enzyme.txt")
enzyme_names <- unique(read.delim("enzyme_names.txt"))
```


```{r, eval=F}
# subset enzymes
#counts <- read_tsv("./humann_gene_family/gene_family_uniref90_level4ec.tsv")
#counts <- read.csv("gene_family_uniref90_level4ec.csv", row.names = 1)
#
#all_species <- data.frame(name=rownames(counts))
#
#enzyme_list <- read_lines("./humann_gene_family/selected_enzyme.txt")
#selected_species <- all_species %>%
#  dplyr::filter(str_detect(name,paste(enzyme_list, collapse = "|") )) %>%
#  pull(name)
#
#sub_counts <- counts %>%
#  rownames_to_column("feature") %>%
#  dplyr::filter(feature %in% selected_species)
#
#write.csv(sub_counts, "gene_family_uniref90_level4ec_subset.csv", quote = F, row.names = F, col.names = T)
#write_tsv(sub_counts, "gene_family_uniref90_level4ec_subset.tsv")

```

```{r}

table(meta$surg_and_wtloss)

```

## Sample frequency by surg_and_wtloss and gender

```{r}

table(meta$surg_and_wtloss, meta$gender)

```
# Differential test

- The score is from logarithmic discriminant analysis (LDA) that measures combined significance and effect size. 

- A positive LDA score mean the abundance is higher in the group 1 (treatment).

- A negative LDA score mean the abundance is higher in the group 0 (pre-surgery).

- The values under two group named columns are the average abundance in that group.

- All tables are sort alphabetically by the row features by default

## post-RYGB (SWL or IWL) vs pre-surgery

```{r, fig.height=10, fig.width=6}
idx <- 1
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL", "RYGB+IWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "RYGB", "RYGB")
meta1$surg_and_wtloss <- tmp_ident


count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"

write.table(count_py1, paste0("./analysis_enzyme/enzyme_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

res <- read.table(paste0("./analysis_enzyme/enzyme_py", idx,".res"), sep = "\t")

STable3_RYGB_sulfide_enzymes <- read.csv("D:/Documents/cankun_hisham/STable3_RYGB_sulfide_enzymes.txt", sep="")
STable3_RYGB_sulfide_enzymes$rm<-1
STable3_RYGB_sulfide_enzymes$Remove <- paste0('f_',STable3_RYGB_sulfide_enzymes$Remove)
STable3_RYGB_sulfide_enzymes$Remove <- gsub("\\.","_",STable3_RYGB_sulfide_enzymes$Remove)
STable3_RYGB_sulfide_enzymes$Remove <- gsub("\\|",".",STable3_RYGB_sulfide_enzymes$Remove)

res_rm<-merge(res,STable3_RYGB_sulfide_enzymes,by.x="V1",by.y="Remove",all.x=T,all.y=T)
rest<-subset(res_rm,is.na(res_rm$rm))
rest$rm<-NULL
res<-rest


rownames(meta1) <- meta1$Sample
seu <- CreateSeuratObject(counts1, meta.data = meta1)
Idents(seu) <- seu$surg_and_wtloss
#####
VlnPlot(seu,c("1.1.1.284-g--Aeromonas.s--Aeromonas-hydrophila"))
#####

ave1 <- AverageExpression(seu, slot = "counts", group.by = "surg_and_wtloss")$RNA
ave1 <- as.data.frame(ave1)
ave1$V1 <- paste0('f-',rownames(ave1))
res1 <- res
res1$V1 <- gsub("\\_","-",res1$V1)
res1$V1 <- gsub("\\|","-",res1$V1)
res1$V1 <- gsub("\\.","-",res1$V1)
ave1$V1 <- gsub("\\_","-",ave1$V1)
ave1$V1 <- gsub("\\|","-",ave1$V1)
ave1$V1 <- gsub("\\.","-",ave1$V1)

res1 <- res1 %>%
  left_join(ave1, by="V1") %>%
  mutate(
    V4 = case_when(
      V3 == 'Pre-surgery' ~ -1 * V4,
      T ~ V4
    )
  ) %>%
  dplyr::select(-V2, -V3)
res1$V1 <- res$V1
colnames(res1) <- c("feature", "LDA score", "adjusted p-val", colnames(ave1)[1], colnames(ave1)[2])

res1 <- res1 %>%
  dplyr::filter(`adjusted p-val` < 0.05 & !is.na(`LDA score`)) 

sig_species <- str_replace_all(res1$feature, "\\.", "\\|")

# DT::datatable(res1, extensions = c('FixedColumns','Buttons'),
#               options = list(
#                 pageLength = 10,
#                 scrollX = TRUE,
#                 scrollCollapse = TRUE,
#                 dom = 'Bfrtip',
#                 buttons = c('copy', 'csv', 'excel')
#               ))
res$V1 <- gsub("f_","",res$V1)
res$V1 <- gsub("\\.","_",res$V1)
res$V1 <- sub("\\_",".",res$V1)
res$V1 <- sub("\\_",".",res$V1)
res$V1 <- sub("\\_",".",res$V1)

res$V1 <- gsub("_g_","|g_",res$V1)
res$V1 <- gsub("_s__",".s__",res$V1)
res$V1 <- gsub("_uncl","|uncl",res$V1)


#res$V1 <- rownames(counts1)
res <- res %>%
  dplyr::filter(`V5` < 0.05 & !is.na(`V4`)) 

rownames(res)<-res$V1

df <- counts1[res$V1,] %>%
  rownames_to_column("name") %>%
  gather(Sample, value,-name) %>%
  left_join(meta1, by = "Sample") %>%
  mutate(enzyme_id = str_split(name, "\\|", simplify = T)[, 1]) %>%
  mutate(feature = str_split(name, "\\|", simplify = T)[, 2]) %>%
  mutate(feature = case_when(feature == "" ~ "sum",
                             T ~ feature)) %>%
  mutate(group =
           case_when(surg_and_wtloss == "RYGB" ~ "post",
                     T  ~ "pre")) %>%
  mutate(xtitle = paste0(enzyme_id, "-" , group)) %>%
  group_by(enzyme_id, group) %>%
  arrange(xtitle, .by_group = TRUE)

res2 <- res1 
res2$enzyme_id <- gsub("f_","",res1$feature)
res2$enzyme_id <- gsub("_","\\.",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.g.*","\\",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.unclassified.*","\\",res2$enzyme_id)
res2<- res2[,c("enzyme_id", "LDA score")]
res22 <- res2 %>% distinct(enzyme_id, .keep_all = T) 

df <- df %>%
  left_join(res22, by="enzyme_id") %>%
  mutate(xlabel = paste0(enzyme_id, " (", formatC(`LDA score`, digits = 3),")"))

#df$value <- log1p(df$value)
df1 <- df %>%
  dplyr::filter(feature != "sum")
df2 <- df %>%
  dplyr::filter(feature == "sum")
length(unique(df1$name))
length(unique(df2$name))
#96 in df1
#17 in df2


new_list<-as.data.frame(unique(df1$name))
colnames(new_list)<-c("name")
new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
new_list$genus <- gsub("\\.s","",new_list$genus)
new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- gsub("\\|g","",new_list$enzyme)

new_list$name <- gsub("_","-",new_list$name)
new_list$name <- gsub("\\|","-",new_list$name)
#df2$newname <- gsub("_","-",df2$name)
#df2$newname <- gsub("\\|","-",df2$newname)

new_list$name2 <- paste0('f-',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
new_list$name2 <- gsub("\\|","\\.",new_list$name2)
new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list$name2 <- gsub("8\\_unclassified","8\\.unclassified",new_list$name2)
new_list$name2 <- gsub("9\\_unclassified","9\\.unclassified",new_list$name2)

new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)


keep<-c("Acidaminococcus","Alistipes","Escherichia","Klebsiella")

new_list_filt<-as.data.frame(new_list[new_list$genus %in% keep, ])


current<-new_list_filt
current<-current[order(current[,'species']), ]
w<-dim(current)
height<- 8*10
width<- 7*12

pdf(paste("barplot/ManualSelectPlots_RYGB_vs_pre_species_trim2_Violin_SelectNotButyrate.pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
gene<-current[i,2]
genus<-current[i,3]
species<-current[i,4]
LDA<-round(current[i,6],3)
p<-round(as.numeric(current[i,7]),4)
enzyme<-current[i,5]

vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
vln_df<-merge(vln_df,meta,by.x=0,by.y="Sample")
rownames(vln_df)<-vln_df$Row.names
vln_df$Row.names<-NULL
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin( trim=TRUE, scale = "width") + geom_jitter(height = 0, width = 0.1, aes(colour = factor(gender),size=5)) + #geom_point(size=5) + 
  scale_colour_manual(name="colour", values=c( "purple", "green")) +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,species,sep=" "))   + 
     theme(text = element_text(size = 40)) 
 #print(s1)
 a1<- s1 + theme(axis.title.y = element_text(size = 40)) + ylab("relative abundance")
 plist[[i]]<-a1  
}
print(wrap_plots(plist,ncol=8,nrow=7))
dev.off()



for (gen in unique(new_list$genus)){
 # gen<-"Streptococcus"
  current<-subset(new_list,new_list$genus==gen)
current<-current[order(current[,'species']), ]
x<-ceiling((dim(current)[1])/3)
height<-10*x
width<-20
if((dim(current)[1])==1){
  height<-8
  width<-9
  }
if((dim(current)[1])==2){
  height<-5
  width<-(20/3)*2
}
if((dim(current)[1])>6){
  height<-20
  width<-20
}
if((dim(current)[1])>9){
  height<-40
  width<-40
}
if((dim(current)[1])==1){
  height<-8
  width<-9
}

pdf(paste("barplot/ManualPlots_RYGB_vs_pre_species_trim2_Violin_",gen,".pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
#i<-1
gene<-current[i,2]
genus<-current[i,3]
species<-current[i,4]
LDA<-round(current[i,6],3)
p<-round(as.numeric(current[i,7]),5)
enzyme<-current[i,5]


#  q<-VlnPlot(seu,features=unique(current$name),combine = T,flip=T) &  theme(axis.title.x = element_blank())
# print(q)
 
 #gene<-"3.1.6.6-g--Bacteroides.s--Bacteroides-xylanisolvens"
 
 
vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin(aes(fill = cluster), trim=TRUE, scale = "width") + geom_jitter() +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,species,sep=" ")) + ylab("relative abundance")
 #print(s1)
 
 plist[[i]]<-s1 
 
}

print(wrap_plots(plist))
dev.off()

  
}


# df1$newname <- gsub("_","-",df1$name)
# df1$newname <- gsub("\\|","-",df1$newname)
# #df2$newname <- gsub("_","-",df2$name)
# #df2$newname <- gsub("\\|","-",df2$newname)
# pdf("barplot/VSG_vs_pre_species_trim2_Violin.pdf",height=20,width=20)
# 
#   #print(VlnPlot(seu,features=unique(df1$newname),combine = T,flip=T))
#   q1<-VlnPlot(seu,features=unique(df1$newname)[1:20],combine = T,flip=T)
#   q2<-VlnPlot(seu,features=unique(df1$newname)[21:40],combine = T,flip=T)
#   q3<-VlnPlot(seu,features=unique(df1$newname)[41:60],combine = T,flip=T)
#   q4<-VlnPlot(seu,features=unique(df1$newname)[61:79],combine = T,flip=T)
#   print(q1)
#  print(q2)
#  print(q3)
#  print(q4)
#  
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
# 
# dev.off()
# df2$newname <- gsub("_","-",df2$name)
# df2$newname <- gsub("\\|","-",df2$newname)
# #df2$newname <- gsub("_","-",df2$name)
# #df2$newname <- gsub("\\|","-",df2$newname)
# pdf("barplot/VSG_vs_pre_sum_trim2_Violin.pdf",height=20,width=20)
# 
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
#  q<- VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T) 
#  print(q)
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
# 
# dev.off()


new_list<-as.data.frame(unique(df2$name))
colnames(new_list)<-c("name")
# new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
# new_list$genus <- gsub("\\.s","",new_list$genus)
# new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
# new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- new_list$name


new_list$name2 <- paste0('f_',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
# new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
# new_list$name2 <- gsub("\\|","\\.",new_list$name2)
# new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
# new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)

temp<-merge(new_list,enzyme_names,by.x="enzyme",by.y="feature")

current<-temp
#current<-current[order(current[,'species']), ]
w<-dim(current)
height<- 3*12
width<- 6*11

pdf(paste("barplot/ManualSelectPlots_RYGB_vs_pre_sum_trim2_Violin_SelectNotButyrate_modEnzName.pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
gene<-current[i,3]

LDA<-round(current[i,4],2)
p<-round(as.numeric(current[i,5]),4)
enzyme<-current[i,1]
enz_name<-current[i,8]

vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
vln_df<-merge(vln_df,meta,by.x=0,by.y="Sample")
rownames(vln_df)<-vln_df$Row.names
vln_df$Row.names<-NULL
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin( trim=TRUE, scale = "width") + geom_jitter(height = 0, width = 0.1, aes(colour = factor(gender),size=5)) +
  scale_colour_manual(name="colour", values=c( "purple", "green")) +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,enz_name,sep=" "))   + 
     theme(text = element_text(size = 40)) 
 #print(s1)
 a1<- s1 + theme(axis.title.y = element_text(size = 40)) + ylab("relative abundance")
 plist[[i]]<-a1  
}
print(wrap_plots(plist),ncol=6,nrow=3)
dev.off()




x<-ceiling((dim(new_list)[1])/3)
height<-10*x
width<-20
if((dim(new_list)[1])==1){
  height<-8
  width<-9
  }
if((dim(new_list)[1])==2){
  height<-5
  width<-(20/3)*2
}
if((dim(new_list)[1])>6){
  height<-20
  width<-20
}
if((dim(new_list)[1])>9){
  height<-40
  width<-40
}
if((dim(new_list)[1])==1){
  height<-8
  width<-9
}


pdf(paste("barplot/ManualPlots_RYGB_vs_pre_sum_trim2_Violin_enzymes",".pdf",sep=""),height=height,width=width)
plist <- list()
##################################################can we change new_list to temp?
for (gen in unique(new_list$enzyme)){
 # gen<-"2.1.1.131"
  current<-subset(new_list,new_list$enzyme==gen)
i<-as.numeric(rownames(current))

#for(i in 1:dim(current)[1]){

gene<-current[1,1]
LDA<-round(current[1,4],3)
p<-round(as.numeric(current[1,5]),5)
enzyme<-current[1,1]
enz_name<-current[i,8]


#  q<-VlnPlot(seu,features=unique(current$name),combine = T,flip=T) &  theme(axis.title.x = element_blank())
# print(q)
 
 #gene<-"3.1.6.6-g--Bacteroides.s--Bacteroides-xylanisolvens"
 
 
vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin(aes(fill = cluster), trim=TRUE, scale = "width") + geom_jitter() +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,enz_name,sep=" ")) + ylab("relative abundance")

 plist[[i]]<-s1 
 #i<-i+1
 
}

print(wrap_plots(plist))
dev.off()


p1 <- ggbarplot(
  df1,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = get_palette("Set1", length(unique(df$feature)))
) +
  rotate_x_text(angle = 45) +
  facet_grid( enzyme_id ~ .,
              scales = "free_x",
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )



p2 <- ggbarplot(
  df2,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = "gray"
) +
  rotate_x_text(angle = 45) +
  facet_grid( enzyme_id ~ .,
              scales = "free_x",
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )

png(
  paste0("./barplot/RYGB_vs_pre_species_trim2.png"),
  width = 4500,
  height = 7500,
  res = 300
)
print(p1)
dev.off()


png(
  paste0("./barplot/RYGB_vs_pre_sum_trim2.png"),
  width = 4500,
  height = 3500,
  res = 300
)
print(p2)
dev.off()

# df3 <- df1 %>%
#   dplyr::select(name, Sample, value, enzyme_id, feature, group, surg_and_wtloss, xtitle) %>%
#   group_by(name, xtitle) %>%
#   summarise(abundance = sum(value))

#write.csv(df3, paste0("./barplot/RYGB_vs_pre_enzyme_by_species_total_abundance.csv"), row.names = F)
write.csv(res1, paste0("./barplot/RYGB_vs_pre_enzyme_by_species_lda_trim2.csv"), row.names = F)

```


## VSG (SWL or IWL)

```{r, fig.height=4, fig.width=6}
idx <- 2
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "VSG+IWL", "VSG+SWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "VSG", "VSG")
meta1$surg_and_wtloss <- as.character(tmp_ident)

count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"
#write.table(count_py1, paste0("./analysis_enzyme/enzyme_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

res <- read.table(paste0("./analysis_enzyme/enzyme_py", idx,".res"), sep = "\t")

STable4_VSG_sulfide_enzymes <- read.csv("D:/Documents/cankun_hisham/STable4_VSG_sulfide_enzymes.txt", sep="")
STable4_VSG_sulfide_enzymes$rm<-1
STable4_VSG_sulfide_enzymes$Remove <- paste0('f_',STable4_VSG_sulfide_enzymes$Remove)
STable4_VSG_sulfide_enzymes$Remove <- gsub("\\.","_",STable4_VSG_sulfide_enzymes$Remove)
STable4_VSG_sulfide_enzymes$Remove <- gsub("\\|",".",STable4_VSG_sulfide_enzymes$Remove)

res_rm<-merge(res,STable4_VSG_sulfide_enzymes,by.x="V1",by.y="Remove",all.x=T,all.y=T)
rest<-subset(res_rm,is.na(res_rm$rm))
rest$rm<-NULL
res<-rest

rownames(meta1) <- meta1$Sample
seu <- CreateSeuratObject(counts1, meta.data = meta1)
Idents(seu) <-  factor(x = seu$surg_and_wtloss, levels = c( 'Pre-surgery','VSG'))
ave1 <- AverageExpression(seu, slot = "counts", group.by = "surg_and_wtloss")$RNA
ave1 <- as.data.frame(ave1)
ave1$V1 <- paste0('f-',rownames(ave1))
res1 <- res
res1$V1 <- gsub("\\_","-",res1$V1)
res1$V1 <- gsub("\\|","-",res1$V1)
res1$V1 <- gsub("\\.","-",res1$V1)
ave1$V1 <- gsub("\\_","-",ave1$V1)
ave1$V1 <- gsub("\\|","-",ave1$V1)
ave1$V1 <- gsub("\\.","-",ave1$V1)
res1 <- res1 %>%
  left_join(ave1, by="V1") %>%
  mutate(
    V4 = case_when(
      V3 == 'Pre-surgery' ~ -1 * V4,
      T ~ V4
    )
  ) %>%
  dplyr::select(-V2, -V3)
res1$V1 <- res$V1
colnames(res1) <- c("feature", "LDA score", "adjusted p-val", colnames(ave1)[1], colnames(ave1)[2])

res1 <- res1 %>%
  dplyr::filter(`adjusted p-val` < 0.05 & !is.na(`LDA score`))

# DT::datatable(res1, extensions = c('FixedColumns','Buttons'),
#               options = list(
#                 pageLength = 10,
#                 scrollX = TRUE,
#                 scrollCollapse = TRUE,
#                 dom = 'Bfrtip',
#                 buttons = c('copy', 'csv', 'excel')
#               ))

res$V1 <- gsub("f_","",res$V1)
res$V1 <- gsub("\\.","_",res$V1)
res$V1 <- sub("\\_",".",res$V1)
res$V1 <- sub("\\_",".",res$V1)
res$V1 <- sub("\\_",".",res$V1)

res$V1 <- gsub("_g_","|g_",res$V1)
res$V1 <- gsub("_s__",".s__",res$V1)
res$V1 <- gsub("_uncl","|uncl",res$V1)
res$V1 <- sub("g__Firmicutes\\|unclassified.s__Firm","g__Firmicutes_unclassified.s__Firm",res$V1)


#res$V1 <- rownames(counts1)
res <- res %>%
  dplyr::filter(`V5` < 0.05 & !is.na(`V4`)) 

rownames(res)<-res$V1
df <- counts1[res$V1, ] %>%
  rownames_to_column("name") %>%
  gather(Sample, value, -name) %>%
  left_join(meta1, by = "Sample") %>%
  mutate(enzyme_id = str_split(name, "\\|", simplify = T)[, 1]) %>%
  mutate(feature = str_split(name, "\\|", simplify = T)[, 2]) %>%
  #dplyr::filter(feature != "") %>%
  mutate(feature = case_when(feature == "" ~ "sum",
                             T ~ feature)) %>%
  mutate(group =
           case_when(surg_and_wtloss == "VSG" ~ "post",
                     T  ~ "pre")) %>%
  mutate(xtitle = paste0(enzyme_id, "-" , group)) %>%
  group_by(enzyme_id, group) %>%
  arrange(xtitle, .by_group = TRUE)

res2 <- res1 
res2$enzyme_id <- gsub("f_","",res1$feature)
res2$enzyme_id <- gsub("_","\\.",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.g.*","\\",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.unclassified.*","\\",res2$enzyme_id)
res2<- res2[,c("enzyme_id", "LDA score")]
res22 <- res2 %>% distinct(enzyme_id, .keep_all = T) 

df <- df %>%
  left_join(res22, by="enzyme_id") %>%
  mutate(xlabel = paste0(enzyme_id, " (", formatC(`LDA score`, digits = 3),")"))

#df$value <- log1p(df$value)
df1 <- df %>%
  dplyr::filter(feature != "sum")
df2 <- df %>%
  dplyr::filter(feature == "sum")
length(unique(df1$name))
length(unique(df2$name))
#79 in df1
#4 in df2

new_list<-as.data.frame(unique(df1$name))
colnames(new_list)<-c("name")
new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
new_list$genus <- gsub("\\.s","",new_list$genus)
new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- gsub("\\|g","",new_list$enzyme)

new_list$name <- gsub("_","-",new_list$name)
new_list$name <- gsub("\\|","-",new_list$name)
#df2$newname <- gsub("_","-",df2$name)
#df2$newname <- gsub("\\|","-",df2$newname)

new_list$name2 <- paste0('f-',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
new_list$name2 <- gsub("\\|","\\.",new_list$name2)
new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list$name2 <- gsub("8\\_unclassified","8\\.unclassified",new_list$name2)
new_list$name2 <- gsub("9\\_unclassified","9\\.unclassified",new_list$name2)

new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)

new_list<-as.data.frame(unique(df1$name))
colnames(new_list)<-c("name")
new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
new_list$genus <- gsub("\\.s","",new_list$genus)
new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- gsub("\\|g","",new_list$enzyme)

new_list$name <- gsub("_","-",new_list$name)
new_list$name <- gsub("\\|","-",new_list$name)
#df2$newname <- gsub("_","-",df2$name)
#df2$newname <- gsub("\\|","-",df2$newname)

new_list$name2 <- paste0('f-',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
new_list$name2 <- gsub("\\|","\\.",new_list$name2)
new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list$name2 <- gsub("8\\_unclassified","8\\.unclassified",new_list$name2)
new_list$name2 <- gsub("9\\_unclassified","9\\.unclassified",new_list$name2)

new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)


keep<-c("Alistipes", "Eggerthella", "Veillonella")
keep2<-c("Streptococcus_vestibularis")

new_list_filt_p1<-as.data.frame(new_list[new_list$genus %in% keep, ])
new_list_filt_p2<-as.data.frame(new_list[new_list$species %in% keep2, ])
new_list_filt<-rbind(new_list_filt_p1,new_list_filt_p2)

current<-new_list_filt
current<-current[order(current[,'species']), ]
w<-dim(current)
height<- 6*10
width<- 5*12

pdf(paste("barplot/ManualSelectPlots_VSG_vs_pre_species_trim2_Violin_SelectNotButyrate_AddStrepV.pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
gene<-current[i,2]
genus<-current[i,3]
species<-current[i,4]
LDA<-round(current[i,6],3)
p<-round(as.numeric(current[i,7]),4)
enzyme<-current[i,5]

vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
vln_df<-merge(vln_df,meta,by.x=0,by.y="Sample")
rownames(vln_df)<-vln_df$Row.names
vln_df$Row.names<-NULL
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin( trim=TRUE, scale = "width") + geom_jitter(height = 0, width = 0.1, aes(colour = factor(gender),size=5)) + #geom_point(size=5) + 
  scale_colour_manual(name="colour", values=c( "purple", "green")) +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,species,sep=" "))   + 
     theme(text = element_text(size = 40)) 
 #print(s1)
 a1<- s1 + theme(axis.title.y = element_text(size = 40)) + ylab("relative abundance")
 plist[[i]]<-a1  
}
print(wrap_plots(plist,ncol=5,nrow=6))#
dev.off()





for (gen in unique(new_list$genus)){
 # gen<-"Streptococcus"
  current<-subset(new_list,new_list$genus==gen)
current<-current[order(current[,'species']), ]
x<-ceiling((dim(current)[1])/3)
height<-10*x
width<-20
if((dim(current)[1])==1){
  height<-8
  width<-9
  }
if((dim(current)[1])==2){
  height<-5
  width<-(20/3)*2
}
if((dim(current)[1])>6){
  height<-20
  width<-20
}
if((dim(current)[1])>9){
  height<-40
  width<-40
}
if((dim(current)[1])==1){
  height<-8
  width<-9
}

pdf(paste("barplot/ManualPlots_VSG_vs_pre_species_trim2_Violin_",gen,".pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
#i<-1
gene<-current[i,2]
genus<-current[i,3]
species<-current[i,4]
LDA<-round(current[i,6],3)
p<-round(as.numeric(current[i,7]),5)
enzyme<-current[i,5]


#  q<-VlnPlot(seu,features=unique(current$name),combine = T,flip=T) &  theme(axis.title.x = element_blank())
# print(q)
 
 #gene<-"3.1.6.6-g--Bacteroides.s--Bacteroides-xylanisolvens"
 
 
vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin(aes(fill = cluster), trim=TRUE, scale = "width") + geom_jitter() +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,species,sep=" ")) + ylab("relative abundance")
 #print(s1)
 
 plist[[i]]<-s1 
 
}

print(wrap_plots(plist))
dev.off()

  
}


# df1$newname <- gsub("_","-",df1$name)
# df1$newname <- gsub("\\|","-",df1$newname)
# #df2$newname <- gsub("_","-",df2$name)
# #df2$newname <- gsub("\\|","-",df2$newname)
# pdf("barplot/VSG_vs_pre_species_trim2_Violin.pdf",height=20,width=20)
# 
#   #print(VlnPlot(seu,features=unique(df1$newname),combine = T,flip=T))
#   q1<-VlnPlot(seu,features=unique(df1$newname)[1:20],combine = T,flip=T)
#   q2<-VlnPlot(seu,features=unique(df1$newname)[21:40],combine = T,flip=T)
#   q3<-VlnPlot(seu,features=unique(df1$newname)[41:60],combine = T,flip=T)
#   q4<-VlnPlot(seu,features=unique(df1$newname)[61:79],combine = T,flip=T)
#   print(q1)
#  print(q2)
#  print(q3)
#  print(q4)
#  
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
# 
# dev.off()
# df2$newname <- gsub("_","-",df2$name)
# df2$newname <- gsub("\\|","-",df2$newname)
# #df2$newname <- gsub("_","-",df2$name)
# #df2$newname <- gsub("\\|","-",df2$newname)
# pdf("barplot/VSG_vs_pre_sum_trim2_Violin.pdf",height=20,width=20)
# 
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
#  q<- VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T) 
#  print(q)
#   #print(VlnPlot(seu,features=unique(df2$newname),combine = T,flip=T))
# 
# dev.off()


new_list<-as.data.frame(unique(df2$name))
colnames(new_list)<-c("name")
# new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
# new_list$genus <- gsub("\\.s","",new_list$genus)
# new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
# new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- new_list$name


new_list$name2 <- paste0('f_',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
# new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
# new_list$name2 <- gsub("\\|","\\.",new_list$name2)
# new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
# new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)
temp<-merge(new_list,enzyme_names,by.x="enzyme",by.y="feature")

current<-temp
#current<-current[order(current[,'species']), ]
w<-dim(current)
height<- 2*10
width<- 2*10

pdf(paste("barplot/ManualSelectPlots_VSG_vs_pre_sum_trim2_Violin_SelectNotButyrate_ModEnzNames.pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
gene<-current[i,3]

LDA<-round(current[i,4],2)
p<-round(as.numeric(current[i,5]),4)
enzyme<-current[i,1]
enz_name<-current[i,8]

vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
vln_df<-merge(vln_df,meta,by.x=0,by.y="Sample")
rownames(vln_df)<-vln_df$Row.names
vln_df$Row.names<-NULL
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin( trim=TRUE, scale = "width") + geom_jitter(height = 0, width = 0.1, aes(colour = factor(gender),size=5)) +
  scale_colour_manual(name="colour", values=c( "purple", "green")) +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,enz_name,sep=" "))    + 
     theme(text = element_text(size = 40)) 
 #print(s1)
 a1<- s1 + theme(axis.title.y = element_text(size = 40)) + ylab("relative abundance")
 plist[[i]]<-a1  
}
print(wrap_plots(plist),ncol=2,nrow=2)
dev.off()



x<-ceiling((dim(new_list)[1])/3)
height<-10*x
width<-20
if((dim(new_list)[1])==1){
  height<-8
  width<-9
  }
if((dim(new_list)[1])==2){
  height<-5
  width<-(20/3)*2
}
if((dim(new_list)[1])>6){
  height<-20
  width<-20
}
if((dim(new_list)[1])>9){
  height<-40
  width<-40
}
if((dim(new_list)[1])==1){
  height<-8
  width<-9
}


pdf(paste("barplot/ManualPlots_VSG_vs_pre_sum_trim2_Violin_enzymes",".pdf",sep=""),height=height,width=width)
plist <- list()

for (gen in unique(new_list$enzyme)){
  #gen<-"2.1.1.131"
  current<-subset(new_list,new_list$enzyme==gen)
i<-as.numeric(rownames(current))

#for(i in 1:dim(current)[1]){

gene<-current[1,3]
LDA<-round(current[1,4],3)
p<-round(as.numeric(current[1,5]),5)
enzyme<-current[1,3]


#  q<-VlnPlot(seu,features=unique(current$name),combine = T,flip=T) &  theme(axis.title.x = element_blank())
# print(q)
 
 #gene<-"3.1.6.6-g--Bacteroides.s--Bacteroides-xylanisolvens"
 
 
vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin(aes(fill = cluster), trim=TRUE, scale = "width") + geom_jitter() +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,"",sep=" ")) + ylab("relative abundance")

 plist[[i]]<-s1 
 #i<-i+1
 
}

print(wrap_plots(plist))
dev.off()


p1 <- ggbarplot(
  df1,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = get_palette("Set1", length(unique(df$feature)))
) +
  rotate_x_text(angle = 45) +
  facet_grid( enzyme_id ~ .,
              scales = "free_x",
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )



p2 <- ggbarplot(
  df2,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = "gray"
) +
  rotate_x_text(angle = 45) +
  facet_grid( enzyme_id ~ .,
              scales = "free_x",
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )

png(
  paste0("./barplot/VSG_vs_pre_species_trim2.png"),
  width = 4500,
  height = 5800,
  res = 300
)
print(p1)
dev.off()


png(
  paste0("./barplot/VSG_vs_pre_sum_trim2.png"),
  width = 4500,
  height = 2000,
  res = 300
)
print(p2)
dev.off()

df3 <- df1 %>%
  dplyr::select(name, Sample, value, enzyme_id, feature, group, surg_and_wtloss, xtitle) %>%
  group_by(name, xtitle) %>%
  summarise(abundance = sum(value))

#write.csv(df3, paste0("./barplot/VSG_vs_pre_enzyme_by_species_total_abundance.csv"), row.names = F)
write.csv(res1, paste0("./barplot/VSG_vs_pre_enzyme_by_species_lda_trim2.csv"), row.names = F)
```



## Females with RYGB SWL vs males with RYGB and SWL 

```{r, fig.height=10, fig.width=6}
idx <- 3
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("RYGB+SWL"))

counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$gender)
#levels(tmp_ident) <- c("Pre-surgery-female", "Surgery-female", "Surgery-female", "Surgery-female", "Surgery-female")
meta1$surg_and_wtloss <- as.character(tmp_ident)
count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"
#write.table(count_py1, paste0("./analysis_enzyme/enzyme_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

res <- read.table(paste0("./analysis_enzyme/enzyme_py", idx,".res"), sep = "\t")

rownames(meta1) <- meta1$Sample
seu <- CreateSeuratObject(counts1, meta.data = meta1)
Idents(seu) <- seu$surg_and_wtloss
ave1 <- AverageExpression(seu, slot = "counts", group.by = "surg_and_wtloss")$RNA
ave1 <- as.data.frame(ave1)
ave1$V1 <- paste0('f-',rownames(ave1))
res1 <- res
res1$V1 <- gsub("\\_","-",res1$V1)
res1$V1 <- gsub("\\|","-",res1$V1)
res1$V1 <- gsub("\\.","-",res1$V1)
ave1$V1 <- gsub("\\_","-",ave1$V1)
ave1$V1 <- gsub("\\|","-",ave1$V1)
ave1$V1 <- gsub("\\.","-",ave1$V1)
res1 <- res1 %>%
  left_join(ave1, by="V1") %>%
  mutate(
    V4 = case_when(
      V3 == 'M' ~ -1 * V4,
      T ~ V4
    )
  ) %>%
  dplyr::select(-V2, -V3)
res1$V1 <- res$V1
colnames(res1) <- c("feature", "LDA score", "adjusted p-val", colnames(ave1)[1], colnames(ave1)[2])

res1 <- res1 %>%
  dplyr::filter(`adjusted p-val` < 0.05 & !is.na(`LDA score`))
  #dplyr::filter(str_detect(feature,paste(species_list, collapse = "|") ))

DT::datatable(res1, extensions = c('FixedColumns','Buttons'),
              options = list(
                pageLength = 10,
                scrollX = TRUE,
                scrollCollapse = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel')
              ))
res$V1 <- rownames(counts1)
res <- res %>%
  dplyr::filter(`V5` < 0.05 & !is.na(`V4`)) 


df <- counts1[res$V1, ] %>%
  rownames_to_column("name") %>%
  gather(Sample, value, -name) %>%
  left_join(meta1, by = "Sample") %>%
  mutate(enzyme_id = str_split(name, "\\|", simplify = T)[, 1]) %>%
  mutate(feature = str_split(name, "\\|", simplify = T)[, 2]) %>%
  #dplyr::filter(feature != "") %>%
    mutate(feature = case_when(feature == "" ~ "sum",
                             T ~ feature)) %>%
  mutate(group = surg_and_wtloss) %>%
  mutate(xtitle = paste0(enzyme_id, "-" , group)) %>%
  group_by(enzyme_id, group) %>%
  arrange(xtitle, .by_group = TRUE)

res2 <- res1 
res2$enzyme_id <- gsub("f_","",res1$feature)
res2$enzyme_id <- gsub("_","\\.",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.g.*","\\",res2$enzyme_id)
res2$enzyme_id <- gsub("\\.unclassified.*","\\",res2$enzyme_id)
res2<- res2[,c("enzyme_id", "LDA score")]
res22 <- res2 %>% distinct(enzyme_id, .keep_all = T) 

df <- df %>%
  left_join(res22, by="enzyme_id") %>%
  mutate(xlabel = paste0(enzyme_id,""))#, " (", formatC(`LDA score`, digits = 3),")"))


#df$value <- log1p(df$value)
df1 <- df %>%
  dplyr::filter(feature != "sum")
df2 <- df %>%
  dplyr::filter(feature == "sum")


new_list<-as.data.frame(unique(df1$name))
colnames(new_list)<-c("name")
new_list$genus <- str_split(new_list$name,"__", simplify = TRUE)[,2]
new_list$genus <- gsub("\\.s","",new_list$genus)
new_list$species <- str_split(new_list$name,"__", simplify = TRUE)[,3]
new_list$enzyme <- str_split(new_list$name,"__", simplify = TRUE)[,1]
new_list$enzyme <- gsub("\\|g","",new_list$enzyme)

new_list$name <- gsub("_","-",new_list$name)
new_list$name <- gsub("\\|","-",new_list$name)
#df2$newname <- gsub("_","-",df2$name)
#df2$newname <- gsub("\\|","-",df2$newname)

new_list$name2 <- paste0('f-',new_list$name)
new_list$name2 <- gsub("\\.","_",new_list$name2)
new_list$name2 <- gsub("\\-g--","\\.g__",new_list$name2)
new_list$name2 <- gsub("\\|","\\.",new_list$name2)
new_list$name2 <- gsub("\\.s--","_s__",new_list$name2)
new_list$name2 <- gsub("\\-","_",new_list$name2)
new_list$name2 <- gsub("8\\_unclassified","8\\.unclassified",new_list$name2)
new_list$name2 <- gsub("9\\_unclassified","9\\.unclassified",new_list$name2)
new_list$name2 <- gsub("4\\_unclassified","4\\.unclassified",new_list$name2)

new_list<-merge(new_list,res1,by.x="name2",by.y="feature",all.x=T)

for (gen in unique(new_list$genus)){
 # gen<-"Streptococcus"
  current<-subset(new_list,new_list$genus==gen)
current<-current[order(current[,'species']), ]
x<-ceiling((dim(current)[1])/3)
height<-10*x
width<-20
if((dim(current)[1])==1){
  height<-8
  width<-9
  }
if((dim(current)[1])==2){
  height<-5
  width<-(20/3)*2
}
if((dim(current)[1])>6){
  height<-20
  width<-20
}
if((dim(current)[1])>9){
  height<-40
  width<-40
}
if((dim(current)[1])==1){
  height<-8
  width<-9
}

pdf(paste("barplot/ManualPlots_Female-RYGB-SWL_vs_Male-RYGB-SW_species_Violin_",gen,".pdf",sep=""),height=height,width=width)
plist <- list()
for(i in 1:dim(current)[1]){
#i<-1
gene<-current[i,2]
genus<-current[i,3]
species<-current[i,4]
LDA<-round(current[i,6],3)
p<-round(as.numeric(current[i,7]),5)
enzyme<-current[i,5]


#  q<-VlnPlot(seu,features=unique(current$name),combine = T,flip=T) &  theme(axis.title.x = element_blank())
# print(q)
 
 #gene<-"3.1.6.6-g--Bacteroides.s--Bacteroides-xylanisolvens"
 
 
vln_df = data.frame(Expression = seu[["RNA"]]@data[gene,], cluster = seu$surg_and_wtloss)
s1<-ggplot(vln_df, aes(x = cluster, y = Expression)) + geom_violin(aes(fill = cluster), trim=TRUE, scale = "width") + geom_jitter() +  theme(axis.title.x = element_blank())+ theme(legend.position = "none")  + labs(title = "",
              subtitle = paste("LDA=",LDA,", adj.p=",p,sep=""),caption = paste(enzyme,species,sep=" ")) + ylab("relative abundance")
 #print(s1)
 
 plist[[i]]<-s1 
 
}

print(wrap_plots(plist))
dev.off()

  
}


p1 <- ggbarplot(
  df1,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = get_palette("Set1", length(unique(df$feature)))
) +
  rotate_x_text(angle = 45) +
  facet_grid( xlabel ~ .,
              scales = "free_x",
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )



p2 <- ggbarplot(
  df2,
  'group',
  'value',
  fill = "feature",
  color = "feature",
  ylab = "Abundance",
  xlab = "",
  palette = "gray"
) +
  rotate_x_text(angle = 45) +
  facet_grid( xlabel ~ .,
              scales = "free_x", 
              # Let the x axis vary across facets.
              space = "free_y",
              # Let the width of facets vary and force all bars to have the same width.
              switch = "y") +
  coord_flip() +
  theme(
    plot.margin = margin(2, 1, 1, 1, "cm"),
    strip.placement = "outside",
    # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),
    # Make facet label background white.
    #axis.title = element_blank(),
    strip.text.y.left = element_text(angle = 0),
    legend.position = "right"
  )

png(
  paste0("./barplot/Female-RYGB-SWL_vs_Male-RYGB-SW_species_mod.png"),
  width = 4500,
  height = 5800,
  res = 300
)
print(p1)
dev.off()


df3 <- df1 %>%
  dplyr::select(name, Sample, value, enzyme_id, feature, group, surg_and_wtloss, xtitle) %>%
  group_by(name, xtitle) %>%
  summarise(abundance = sum(value))

#write.csv(df3, paste0("./barplot/VSG_vs_pre_enzyme_by_species_total_abundance.csv"), row.names = F)
write.csv(res1, paste0("./barplot/Female-RYGB-SWL_vs_Male-RYGB-SW_lda.csv"), row.names = F)

```