---
title: "Species abundance analysis"
author: "Cankun Wang"
date: "`r format(Sys.time(), '%m/%d/%Y')`"
output: 
  html_document:
    toc: true
    toc_float: false
    number_sections: true
    code_folding: hide
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
# Hide all warnings and messages, show code
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = F)

bioc_packages <- c("EnhancedVolcano")
cran_packages <- c("enrichR",
                   "ggpubr",
                   "pheatmap",
                   "ggplot2",
                   "VennDiagram",
                   "stringr",
                   "here")
bioc_np <-
  bioc_packages[!(bioc_packages %in% installed.packages()[, "Package"])]
cran_np <-
  cran_packages[!(cran_packages %in% installed.packages()[, "Package"])]
if (!require("BiocManager"))
  install.packages("BiocManager")

if (length(cran_np)) {
  install.packages(cran_np)
}

if (length(bioc_np)) {
  BiocManager::install(bioc_np)
}

# 'here' pacakge automatically sets working directory for us
library(here)
# DESeq2 provides methods to test for differential gene expression (DGE) analysis 
library(DESeq2)
# ‘ggplot2’ and its extension for publication ready plots
library(ggplot2)
library(ggpubr) 
# Volcano plot
library(EnhancedVolcano) 
# Heatmap
library(pheatmap) 
# enrichR provides functional gene set enrichment analysis
library(enrichR) 

library(phyloseq)

theme_set(theme_bw())
fontsize = 18L
theme_update(axis.title.x = element_text(size=fontsize))
theme_update(axis.title.y = element_text(size=fontsize))
theme_update(plot.title = element_text(size=fontsize+2))
library(lefser)
library(Seurat)
library(tidyverse)
```

# Load data

Sample 126, 128, 129, 131, 132, 139 are removed from analysis

```{r}

counts <- read.csv("species_abundance.csv", row.names = 1)

# Read metadata
meta <- read.csv("meta_v2.csv", stringsAsFactors = F)

remove_idx <- which(meta$ID %in% c(126, 128, 129, 131, 132, 139))

counts <- counts[, -remove_idx]
meta <- meta[-remove_idx,]

surg <- str_split_fixed(meta$surg_and_wtloss, "\\+", 2)[,1]
wtloss <- str_split_fixed(meta$surg_and_wtloss, "\\+", 2)[,2]
wtloss <-gsub("^$","Pre-surgery", wtloss)

counts_py_raw <- read.csv("species_abundance.csv", header = F, row.names = 1)
#count_py <- rbind(surg, wtloss, counts_py_raw)
count_py <- rbind(meta$surg_and_wtloss, counts_py_raw)

rownames(count_py)[1] <- "surg"
rownames(count_py)[2] <- "wtloss"

#write.csv(count_py, "species_py.csv", row.names = T, col.names = F, quote = F)
#write.table(count_py, "species_py.txt", row.names = T, col.names = F, quote = F, sep="\t")

```


```{r}

DT::datatable(meta, extensions = c('FixedColumns','Buttons'),
              options = list(
                pageLength = 10,
                scrollX = TRUE,
                scrollCollapse = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel')
              ))
```

## Sample frequency by surg_and_wtloss

```{r}

table(meta$surg_and_wtloss)

```

## Sample frequency by surg_and_wtloss and gender

```{r}

table(meta$surg_and_wtloss, meta$gender)

```


# Differential test

- The score is from logarithmic discriminant analysis (LDA) that measures combined significance and effect size. 

- A positive LDA score mean the abundance is higher in the group 1 (treatment).

- A negative LDA score mean the abundance is higher in the group 0 (pre-surgery).

- The values under two group named columns are the average abundance in that group.

- All tables are sort alphabetically by the row features by default

## RYGB (SWL or IWL)

```{r, fig.height=6, fig.width=6}
idx <- 1
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL", "RYGB+IWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "RYGB (SWL or IWL)", "RYGB (SWL or IWL)")
meta1$surg_and_wtloss <- tmp_ident


count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"

count_py2 <- count_py1 %>%
  rownames_to_column("col") %>%
  dplyr::filter(str_detect(col, "s__")) %>%
  column_to_rownames("col")
write.table(count_py2, paste0("./analysis/species_py1", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

write.table(count_py1, paste0("./analysis/species_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

res <- read.table(paste0("./analysis/species_py", idx,".res"), sep = "\t")


obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)
lefserPlot(res, trim.names = TRUE)


res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))  %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```

## VSG (SWL or IWL)

```{r, fig.height=4, fig.width=6}
idx <- 2
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "VSG+IWL", "VSG+SWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "VSG (SWL or IWL)", "VSG (SWL or IWL)")
meta1$surg_and_wtloss <- as.character(tmp_ident)

count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"
write.table(count_py1, paste0("./analysis/species_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")

obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)

res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```


## Bariatric surgery with IWL (RYGB or VSG) 

```{r, fig.height=6, fig.width=6}
idx <- 3
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+IWL", "VSG+IWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "IWL (RYGB or VSG)", "IWL (RYGB or VSG)")
meta1$surg_and_wtloss <- factor(tmp_ident, levels = levels(tmp_ident)[c(1, 2)])

obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)

res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))  %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE))  
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```


## Bariatric surgery with SWL (RYGB or VSG) 

```{r, fig.height=6, fig.width=6}
idx <- 4
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL", "VSG+SWL"))
counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery", "SWL (RYGB or VSG)", "SWL (RYGB or VSG)")
meta1$surg_and_wtloss <- as.character(tmp_ident)

obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)

res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```

## Male with Bariatric surgery 

ERROR: unable to process, possibly due to small number of pre-surgery-male group sample size

- Total samples: 5
- Pre-surgery(male): 2
- Surgery-male: 3


```{r, fig.height=6, fig.width=6, eval=F}
idx <- 5
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL", "VSG+SWL", "RYGB+IWL", "VSG+IWL")) %>%
  filter(gender == 'M')

counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery-male", "Surgery-male")
meta1$surg_and_wtloss <- as.character(tmp_ident)

count_py1 <- rbind(as.character(meta1$surg_and_wtloss), colnames(counts1), counts1)
rownames(count_py1)[1] <- "condition"
rownames(count_py1)[2] <- "sample_id"

write.table(count_py1, paste0("./analysis/species_py", idx,".txt"), row.names = T, col.names = F, quote = F, sep="\t")
table(meta1$surg_and_wtloss)
obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)

res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```

## Female with Bariatric surgery 

```{r, fig.height=6, fig.width=6}
idx <- 6
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL", "VSG+SWL", "RYGB+IWL", "VSG+IWL")) %>%
  filter(gender == 'F')

counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
levels(tmp_ident) <- c("Pre-surgery-female", "Surgery-female", "Surgery-female", "Surgery-female", "Surgery-female")
meta1$surg_and_wtloss <- as.character(tmp_ident)

obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)


res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```

## Females with RYGB SWL pre- vs post

```{r, fig.height=6, fig.width=6}
idx <- 7
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("Pre-surgery", "RYGB+SWL")) %>%
  filter(gender == 'F')

counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$surg_and_wtloss)
#levels(tmp_ident) <- c("Pre-surgery-female", "Surgery-female", "Surgery-female", "Surgery-female", "Surgery-female")
meta1$surg_and_wtloss <- as.character(tmp_ident)
obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)


res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```

## Females with RYGB SWL vs males with RYGB and SWL 

```{r, fig.height=4, fig.width=6}
idx <- 8
meta1 <- meta %>%
  filter(surg_and_wtloss %in% c("RYGB+SWL"))

counts1 <- counts[ , meta1$Sample]

tmp_ident <- as.factor(meta1$gender)
#levels(tmp_ident) <- c("Pre-surgery-female", "Surgery-female", "Surgery-female", "Surgery-female", "Surgery-female")
meta1$surg_and_wtloss <- as.character(tmp_ident)
obj <- SummarizedExperiment(assays=list(counts=counts1),colData=meta1)
res <- lefser(obj, groupCol = "surg_and_wtloss", lda.threshold = 0.1)


#lefserPlot(res)


res_g<- res %>% dplyr::filter(str_detect(Names, "g__"))   %>% dplyr::filter(str_detect(Names, "s__", negate = TRUE)) 
lefserPlot(res_g, trim.names = TRUE)

res_s<- res %>% dplyr::filter(str_detect(Names, "s__")) 
lefserPlot(res_s, trim.names = TRUE)

```
